Technical Report

### 2018-05-29 fully-abstract-comp/ftlr-proof-cases.tex
Updated ftlr cases to let failing happen in a number of steps.
Added some more to the call case in the refactoring.
Add some more lemmas about splittability, shrinkability and purity of permission-based conditions and the value relation.

\begin{lemma}[non-linear words are pure]
  \label{lem:non-linear-pure}
  If $\npair{(w_1,w_2)} \in \lrv(H_\sigma,W)$ and ($\nonLinear{w_1}$ or $\nonLinear{w_2}$), then
  $\npair{(w_1,w_2)} \in \lrv(H_\sigma,\purePart{W})$.
\end{lemma}
\begin{proof}
  Follows easily by inspecting the definitions of $\lrv$, $\readCond[]{}$, $\addressable{}$, $\writeCond[]{}$, $\execCond[]{}$ and $\xReadCond[]{}$ and using Lemma~\ref{lem:purePart-idempotent}.
\end{proof}

@@

  \item \label{case:ftlr:failed} $\Phi_S \step[\gc] \failed$ and $\Phi_T \step\failed$

@@

    \item TODO: other useful info

>>>>

@@

  \item \label{case:ftlr:failed} $\Phi_S \step[\gc] \failed$ and $\Phi_T
    \step[i] \failed$ for some $i$.

@@

    \item $\Phi_S \step[\gc] \Phi_S' \neq \failed$
    \item $\Phi_T \step \Phi_T' \neq \failed$
    \item $\Phi_T' = \updPc{\Phi_T\updReg{\rtmp{1}}{z}}$
    \item $\Phi_S(r_1) = \sealed{\sigma,c_1}$
    \item $\Phi_S(r_2) = \sealed{\sigma,c_2}$
    \item $\nonExec{c_2}$
    \item $\Phi_S(\stk) = \stkptr{\rw, \baddr_\stk, \eaddr_\stk, \aaddr_\stk}$
    \item $\baddr_\stk < \aaddr_\stk \leq \eaddr_\stk$
    \item $\Phi_S(\pcreg) = ((\perm,\lin),\baddr,\eaddr,\aaddr)$
    \item $w_1 = \linCons{c_1}$ and $w_2 = \linCons{c_2}$
    \item
          \Phi_S'.\reg = \Phi_S.\reg
          &[\pcreg \mapsto c_1] \\
          &[\rdata \mapsto c_2] \\
          &[\rstk \mapsto \stkptr{\rw,\baddr_\stk,\aaddr_\stk-1,\aaddr_\stk-1}] \\
          &[\rretc \mapsto \sealed{\sigma',\retptrc{\baddr,\eaddr,\aaddr+\calllen}}]\\
          &[\rretd \mapsto \sealed{\sigma',\retptrd{\aaddr_\stk,\eaddr_\stk}}] \\
          &[r_1,r_2 \mapsto w_1,w_2] \\
          &[\rtmp{1} \mapsto 0]
    \item $\Phi_S'.\mem = \Phi_S.\mem$
    \item $\Phi_S'.\stk = ((\aaddr+\calllen),\ms_\stk |_{\aaddr_\stk,\eaddr_\stk}\update{\aaddr_\stk}{42}) :: \Phi_S.\stk$
    \item $\Phi_S'.\ms_\stk = \Phi_S.\ms_\stk = \ms_\stk - \ms_\stk|_{\aaddr_\stk,\eaddr_\stk}$
    \item $\mem(\aaddr+\offpc) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma_\aaddr}$
    \item $\sigma' = \sigma_\aaddr + \offsigma$
    \item $\sigma_\aaddr \leq \sigma' \leq \sigma_\eaddr$

### 2018-05-29 fully-abstract-comp/technical-report.tex
Fix splittability of readCond and writeCond and xReadCond.
Proposal for making execCond splittable.
Add some more lemmas about splittability, shrinkability and purity of permission-based conditions and the value relation.

Source language:
\begin{itemize}
\item Variable length instructions that match the length of the compiled instructions
  \begin{itemize}
%  \item Opaque capabilities do not hide the length of a program (especially an issue if we ever hope to have error recovery).
  \item This is needed for correctness. See subsection~\ref{subsec:capability-opacity} for an example it helps prevent.
  \item It is only used for the call instruction.
  \end{itemize}
% Lau: 18-12-2017: I do not think this is true anymore?
% \item Programs have undefined behavior when passing ret/stk pointers.[\aaddr,\baddr]
\end{itemize}

@@

      % This case was never used (?) so it is not necessary.
      % \wedge \\
      % \quad \npair[n']{\src{\vsc_S'},\src{\vsc_S},\vsc_T',\vsc_T} \in \lrexj(W' \oplus W_o)
    \end{array}
    \right\}\cup\\
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{\seal{\sigma,\sigma_\baddr,\sigma_\eaddr}},\\ \seal{\sigma,\sigma_\baddr,\sigma_\eaddr} \endarray \right)} 
    \; \middle| \;
    \begin{array}{l}
      \forall \sigma' \in [\sigma_\baddr,\sigma_\eaddr] \ldotp \exists r \in \dom(\pwheap) \ldotp \\
      \quad \pwheap(r) = (\pure,\_,H_\sigma) \tand H_\sigma \; \sigma' \nequal \lrv
    \end{array}
    \right\} \cup \\
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{\stkptr{\perm,\baddr,\eaddr,\aaddr}},\\ ((\perm,\linear),\baddr,\eaddr,\aaddr) \endarray \right)} \;\middle|\;
    \begin{array}{l}
      \begin{array}{r l l}
        \perm = \noperm & \Rightarrow & \npair{(\linear,\baddr,\eaddr)} \in \lrp(W) \wedge \\
        \perm \in \readAllowed{} &\Rightarrow& \npair{[\baddr,\eaddr]} \in \stackReadCond{W} \wedge \\
        \perm \in \writeAllowed{} &\Rightarrow& \npair{[\baddr,\eaddr]} \in \stackWriteCond{W}
      \end{array}
    \end{array}
    \right\} \cup \\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{((\perm,\lin),\baddr,\eaddr,\aaddr)},\\ ((\perm,\lin),\baddr,\eaddr,\aaddr) \endarray \right)} \;\middle|\; 
    \begin{array}{l}
      \begin{array}{r l l }
        \perm = \noperm & \Rightarrow & \npair{(\lin,\baddr,\eaddr)} \in \lrp(W) \wedge \\
        \perm \in \readAllowed{} &\Rightarrow& \npair{[\baddr,\eaddr]} \in \readCond{\lin,W} \wedge\\
        \perm \in \writeAllowed{} &\Rightarrow& \npair{[\baddr,\eaddr]} \in \writeCond{\lin,W} \wedge\\
        % we are excluding rwx pointers.
        \perm \neq \rwx \wedge \\
        % \perm = \rwx &\Rightarrow& \array[t]{l}\npair{(\{\rwx,\rx\},\baddr,\eaddr)} \in \execCond{\lin,W} \wedge \\
        %                            \npair{(\baddr,\eaddr)} \in \xReadCond{\lin,W} \endarray\\
        \perm = \rx &\Rightarrow& \array[t]{l}\npair{(\{\rx\},\baddr,\eaddr)} \in \execCond{\lin,W} \wedge\\
                                  \npair{[\baddr,\eaddr]} \in \xReadCond{\lin,W}\endarray
      \end{array}
    \end{array}
    \right\}
  \end{array}
\]

@@

\[
  \readCond{\lin,W} = \left\{ \npair{A} \middle| 
    \begin{array}{l}
      \exists S \subseteq \addressable{\lin, \pwheap} \ldotp \\
      \quad \exists R : S \fun \powerset{\nats} \\
      \qquad \biguplus_{r\in S} R(r) \supseteq A \wedge\\
      \qquad \quad \forall r \in S \ldotp \pwheap(r) \nsubeq \stdreg{R(r),\gc}{\pur}
    \end{array}
  \right\}
\]
\lau{RESOLVED: Make this condition require a set of adjacent regions. Check whether needed for the stack condition.}
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.
\[
  \stackReadCond{W} = \left\{ \npair{A} \middle| 
    \begin{array}{l}
      \exists S \subseteq \addressable{\lin, \pwfree} \ldotp \\
      \quad \exists R : S \fun \powerset{\nats} \\
      \qquad \biguplus_{r\in S} R(r) \supseteq A \wedge \\
      \qquad \quad \forall r \in S \ldotp \pwfree(r) \nsubeq \stdreg{R(r),\gc}{\pur}
    \end{array}
  \right\}
\]
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.
\[
  \xReadCond{\lin,W} = \left\{ \npair{A} \middle| 
    \begin{array}{l}
      \exists S \subseteq \addressable{\lin, \pwfree} \ldotp \\
      \quad \exists M : S \fun \powerset{\MemSeg} \\
      \qquad \biguplus_{r\in S} \dom(M(r)) \supseteq A \wedge\\
      % \qquad \biguplus_{r\in S} R(r) \# \biguplus_{r\in S} C(r) \wedge \\
      \qquad \quad \forall r \in S \ldotp  \pwheap(r) \nequal \codereg{\_,\_,M(r),\gc}
    \end{array}
  \right\}
\]
\lau{RESOLVED: Make this condition require a set of adjacent regions.}
\lau{TODO: allow code regions to be merged into one. Allow for (... forgot to write the rest, but probably related to splicing regions.) }

@@

\[
  \writeCond{\lin,W} = \left\{ \npair{A} \middle| 
    \begin{array}{l}
      \exists S \subseteq \addressable{\lin, \pwheap} \ldotp \\
      \quad \exists R : S \fun \powerset{\nats} \\
      \qquad \biguplus_{r\in S} R(r) \supseteq A \wedge\\
      \qquad \quad \forall r \in S \ldotp \pwheap(r) \nsupeq \stdreg{R(r),\gc}{\pur} \wedge\\
      \qquad \quad \pwheap(r) \text{ is address-stratified}
    \end{array}
  \right\}
\]
\lau{TODO: Make this condition require a set of adjacent regions. Check whether necessary for the stack region.}
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.
% \dominique{Why $n-1$ above?  There is already a quantification over $n' <n$ in the memory satisfaction relation and another $n-1$ is used in $\stdreg{[\baddr',\eaddr'],\gc}{\pur}$. Also: readCond doesn't have the $n-1$. Update: the memory satisfaction was updated by Lau to remove the quantification over $n' < n$ and I dropped the $n-1$ here.}
\[
  \stackWriteCond{W} = \left\{ \npair{[\baddr,\eaddr]}) \middle| 
    \begin{array}{l}
      \exists S \subseteq \addressable{\lin, \pwfree} \ldotp \\
      \quad \exists R : S \fun \powerset{\nats} \\
      \qquad \biguplus_{r\in S} R(r) \supseteq [\baddr,\eaddr] \wedge \\
      \qquad \quad \forall r \in S \ldotp \pwfree(r) \nsupeq \stdreg{R(r),\gc}{\pur} \wedge\\
      \qquad \quad \pwfree(r) \text{ is address-stratified}
    \end{array}
  \right\}
\]
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.

@@

% \dominique{22-1-2018: the below is an alternative proposal to the above definition. It is part of a proposed refactoring to simplify the merge the cases for return pointers and closures in the value relation.}
Note: this new version of execCond uses the expression relation for regular jumps since it expresses the validity of jumping to an address pointed to by an executable capability. 
\[
  \execCond{\lin,W} = \left\{ \npair{(\baddr,\eaddr)} \middle|
    \begin{array}{l}
      \forall W_l \ldotp\\
      \quad ((W_l = \purePart{W} \wedge \lin = \normal) \vee (W_l = W \wedge \lin = \linear)) \wedge\\
      \quad \forall n' < n, W' \future W_l, \aaddr \in [\baddr',\eaddr'] \subseteq [\baddr,\eaddr] \ldotp\\
      \qquad \npair[n']{\stpair[.]{((\rx,\lin),\baddr',\eaddr',\aaddr)}{((\rx,\lin),\baddr',\eaddr',\aaddr)}} \in \lre(W')
    \end{array}
    \right\}
\]

@@

\begin{lemma}[readCond shrinkable]
  \label{lem:readCond-shrinkable}
  If $\npair{A} \in \readCond{\lin,W}$  and $A' \subseteq A$, then
  $\npair{A'} \in \readCond{\lin,W}$.
\end{lemma}
\begin{proof}
  Follows easily from the definition.
\end{proof}

\begin{lemma}[readXCond shrinkable]
  \label{lem:readXCond-shrinkable}
  If $\npair{A} \in \xReadCond{\lin,W}$  and $A' \subseteq A$, then
  $\npair{A'} \in \xReadCond{\lin,W}$.
\end{lemma}
\begin{proof}
  Follows easily from the definition.
\end{proof}

@@

  then $\npair{(w,w)} \in \lrvg{\trust}(W)$.
\end{lemma}
\begin{proof}
  We distinguish two cases:
  \begin{itemize}
  \item $\trust = \untrusted$ and $\dom(\mscode \mathrel{\#} \ta)$:
    By definition of $\lrv(W)$, it suffices to show that:
    \begin{itemize}
    \item $\npair{[b,e]}\in\readCond{\normal,W}$:
      this follows from Lemma~\ref{lem:code-memory-untrusted-readable}.
    \item $\npair{[b,e]}\in\xReadCond{\normal,W}$:
      follows from the definition of $\xReadCond$, together with the assumption that $\pwheap(r_{\mathrm{code}}) = \codereg{\sigrets,\sigcloss,\mscode,\gc}$.
    \item $\npair{[b,e]}\in\execCond{\normal,W}$:
      take $n' < n$, $W' \future \purePart{W}$, $\aaddr' \in [\baddr',\eaddr'] \subseteq [\baddr,\eaddr]$ and $w' = ((\rx,\normal),\baddr',\eaddr',\aaddr')$.
      Then we need to show that $\npair[n']{(w',w')} \in \lre(W')$.
      This now follows immediately from the (regular) FTLR (Theorem~\ref{thm:ftlr}), using the two above points, Lemma~\ref{lem:downwards-closed} and Lemmas~\ref{lem:readCond-shrinkable} and~\ref{lem:readXCond-shrinkable}.
    \end{itemize}

>>>>

Source language:
\begin{itemize}
\item Variable length instructions that match the length of the compiled instructions
  \begin{itemize}
%  \item Opaque capabilities do not hide the length of a program (especially an issue if we ever hope to have error recovery).
  \item This is needed for correctness. %See subsection~\ref{subsec:capability-opacity} for an example it helps prevent.
  \item It is only used for the call instruction.
  \end{itemize}
% Lau: 18-12-2017: I do not think this is true anymore?
% \item Programs have undefined behavior when passing ret/stk pointers.[\aaddr,\baddr]
\end{itemize}

@@

      % This case was never used (?) so it is not necessary.
      % \wedge \\
      % \quad \npair[n']{\src{\vsc_S'},\src{\vsc_S},\vsc_T',\vsc_T} \in \lrexj(W' \oplus W_o)
    \end{array}
    \right\}\cup\\
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{\seal{\sigma,\sigma_\baddr,\sigma_\eaddr}},\\ \seal{\sigma,\sigma_\baddr,\sigma_\eaddr} \endarray \right)} 
    \; \middle| \;
    \begin{array}{l}
      \forall \sigma' \in [\sigma_\baddr,\sigma_\eaddr] \ldotp \exists r \in \dom(\pwheap) \ldotp \\
      \quad \pwheap(r) = (\pure,\_,H_\sigma) \tand H_\sigma \; \sigma' \nequal \lrv
    \end{array}
    \right\} \cup \\
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{\stkptr{\perm,\baddr,\eaddr,\aaddr}},\\ ((\perm,\linear),\baddr,\eaddr,\aaddr) \endarray \right)} \;\middle|\;
    \begin{array}{l}
      \begin{array}{r l l}
        \perm = \noperm & \Rightarrow & \npair{(\linear,\baddr,\eaddr)} \in \lrp(W) \wedge \\
        \perm \in \readAllowed{} &\Rightarrow& \npair{[\baddr,\eaddr]} \in \stackReadCond{W} \wedge \\
        \perm \in \writeAllowed{} &\Rightarrow& \npair{[\baddr,\eaddr]} \in \stackWriteCond{W}
      \end{array}
    \end{array}
    \right\} \cup \\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{((\perm,\lin),\baddr,\eaddr,\aaddr)},\\ ((\perm,\lin),\baddr,\eaddr,\aaddr) \endarray \right)} \;\middle|\; 
    \begin{array}{l}
      \begin{array}{r l l }
        \perm = \noperm & \Rightarrow & \npair{(\lin,\baddr,\eaddr)} \in \lrp(W) \wedge \\
        \perm \in \readAllowed{} &\Rightarrow& \npair{[\baddr,\eaddr]} \in \readCond{\lin,W} \wedge\\
        \perm \in \writeAllowed{} &\Rightarrow& \npair{[\baddr,\eaddr]} \in \writeCond{\lin,W} \wedge\\
        % we are excluding rwx pointers.
        \perm \neq \rwx \wedge \\
        % \perm = \rwx &\Rightarrow& \array[t]{l}\npair{(\{\rwx,\rx\},\baddr,\eaddr)} \in \execCond{\lin,W} \wedge \\
        %                            \npair{(\baddr,\eaddr)} \in \xReadCond{\lin,W} \endarray\\
        \perm = \rx &\Rightarrow& \array[t]{l}\npair{[\baddr,\eaddr]} \in \execCond{\lin,W} \wedge\\
                                  \npair{[\baddr,\eaddr]} \in \xReadCond{\lin,W}\endarray
      \end{array}
    \end{array}
    \right\}
  \end{array}
\]

@@

\[
  \readCond{\lin,W} = \left\{ \npair{A} \middle| 
    \begin{array}{l}
      \exists S \subseteq \addressable{\lin, \pwheap} \ldotp \\
      \quad \exists R : S \fun \powerset{\nats} \\
      \qquad \biguplus_{r\in S} R(r) \supseteq A \wedge\\
      \qquad \lin = \linear \Rightarrow \forall r\ldotp |R(r)|  = 1\\
      \qquad \quad \forall r \in S \ldotp \pwheap(r) \nsubeq \stdreg{R(r),\gc}{\pur}
    \end{array}
  \right\}
\]
\lau{RESOLVED: Make this condition require a set of adjacent regions. Check whether needed for the stack condition.}
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.
\[
  \stackReadCond{W} = \left\{ \npair{A} \middle| 
    \begin{array}{l}
      \exists S \subseteq \addressable{\lin, \pwfree} \ldotp \\
      \quad \exists R : S \fun \powerset{\nats} \\
      \qquad \biguplus_{r\in S} R(r) \supseteq A \wedge \\
      \qquad \quad \forall r \in S \ldotp \pwfree(r) \nsubeq \stdreg{R(r),\gc}{\pur}
    \end{array}
  \right\}
\]
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.
\[
  \xReadCond{\lin,W} = \left\{ \npair{A} \middle| 
    \begin{array}{l}
      \exists S \subseteq \addressable{\lin, \pwfree} \ldotp \\
      \quad \exists M : S \fun \powerset{\MemSeg} \\
      \qquad \biguplus_{r\in S} \dom(M(r)) \supseteq A \wedge\\
      \qquad \lin = \linear \Rightarrow \forall r\ldotp |R(r)|  = 1\\
      % \qquad \biguplus_{r\in S} R(r) \# \biguplus_{r\in S} C(r) \wedge \\
      \qquad \quad \forall r \in S \ldotp  \pwheap(r) \nequal \codereg{\_,\_,M(r),\gc}
    \end{array}
  \right\}
\]
\lau{RESOLVED: Make this condition require a set of adjacent regions.}
\lau{TODO: allow code regions to be merged into one. Allow for (... forgot to write the rest, but probably related to splicing regions.) }

@@

\[
  \writeCond{\lin,W} = \left\{ \npair{A} \middle| 
    \begin{array}{l}
      \exists S \subseteq \addressable{\lin, \pwheap} \ldotp \\
      \quad \exists R : S \fun \powerset{\nats} \\
      \qquad \biguplus_{r\in S} R(r) \supseteq A \wedge\\
      \qquad \lin = \linear \Rightarrow \forall r\ldotp |R(r)|  = 1\\
      \qquad \quad \forall r \in S \ldotp \pwheap(r) \nsupeq \stdreg{R(r),\gc}{\pur} \wedge\\
      \qquad \quad \pwheap(r) \text{ is address-stratified}
    \end{array}
  \right\}
\]
\lau{TODO: Make this condition require a set of adjacent regions. Check whether necessary for the stack region.}
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.
% \dominique{Why $n-1$ above?  There is already a quantification over $n' <n$ in the memory satisfaction relation and another $n-1$ is used in $\stdreg{[\baddr',\eaddr'],\gc}{\pur}$. Also: readCond doesn't have the $n-1$. Update: the memory satisfaction was updated by Lau to remove the quantification over $n' < n$ and I dropped the $n-1$ here.}
\[
  \stackWriteCond{W} = \left\{ \npair{[\baddr,\eaddr]}) \middle| 
    \begin{array}{l}
      \exists S \subseteq \addressable{\lin, \pwfree} \ldotp \\
      \quad \exists R : S \fun \powerset{\nats} \\
      \qquad \biguplus_{r\in S} R(r) \supseteq [\baddr,\eaddr] \wedge \\
      \qquad \quad \forall r \in S \ldotp \pwfree(r) \nsupeq \stdreg{R(r),\gc}{\pur} \wedge\\
      \qquad \quad \pwfree(r) \text{ is address-stratified}
    \end{array}
  \right\}
\]
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.

@@

% \dominique{22-1-2018: the below is an alternative proposal to the above definition. It is part of a proposed refactoring to simplify the merge the cases for return pointers and closures in the value relation.}
Note: this new version of execCond uses the expression relation for regular jumps since it expresses the validity of jumping to an address pointed to by an executable capability. 
\begin{align*}
  \execCond{\lin,W} &=
  \left\{ \npair{A} \middle|
    \begin{array}{l}
      \forall n' < n, W' \future \purePart{W}, \aaddr \in [\baddr',\eaddr'] \subseteq A \ldotp\\
      \quad \npair[n']{\stpair[.]{((\rx,\lin),\baddr',\eaddr',\aaddr)}{((\rx,\lin),\baddr',\eaddr',\aaddr)}} \in \lre(W')
    \end{array}
    \right\}\\
  &\cup\left\{ \npair{A} \middle|
    \begin{array}{l}
      \lin = \linear \wedge\\
      \exists W_a : A \fun \World \wedge W = \oplus_{a\in[\baddr,\eaddr]} W_a(a)\wedge\\
      \forall n' < n, \aaddr\in[\baddr',\eaddr'] \subseteq A, W' \future \oplus_{a\in[\baddr',\eaddr']} W_a(a), \ldotp\\
      \quad \npair[n']{\stpair[.]{((\rx,\lin),\baddr',\eaddr',\aaddr)}{((\rx,\lin),\baddr',\eaddr',\aaddr)}} \in \lre(W')
    \end{array}
    \right\}
\end{align*}

@@

\begin{lemma}[non-linear words are pure]
  \label{lem:non-linear-pure}
  \begin{itemize}
  \item If $\npair{A} \in \readCond{\normal,W}$, then $\npair{A} \in \readCond{}(\normal, \purePart{W} )$.
  \item If $\npair{A} \in \writeCond{\normal,W}$, then $\npair{A} \in \writeCond{}(\normal,\purePart{W})$
  \item If $\npair{A} \in \execCond{\normal,W}$, then $\npair{A} \in \execCond{}(\normal,\purePart{W})$
  \item If $\npair{(w_1,w_2)} \in \lrv(H_\sigma,W)$ and ($\nonLinear{w_1}$ or
    $\nonLinear{w_2}$), then
    $\npair{(w_1,w_2)} \in \lrv(H_\sigma,\purePart{W})$.
  \end{itemize}
\end{lemma}
\begin{proof}
  Follows easily by inspecting the definitions of $\lrv$, $\readCond[]{}$, $\addressable{}$, $\writeCond[]{}$, $\execCond[]{}$ and $\xReadCond[]{}$ and using Lemma~\ref{lem:purePart-idempotent}.
\end{proof}

\begin{lemma}[permission-based conditions splittable]
  \label{lem:conds-splittable}
  If $A = [\baddr_1,\eaddr_1] \uplus [\baddr_2,\eaddr_2]$, then
  \begin{itemize}
  \item If $\npair{A} \in \readCond{\lin,W}$, then there exists $W_1, W_2$ such that $W = W_1\oplus W_2$ such that $\npair{[\baddr_1,\eaddr_1]} \in \readCond{\lin,W_1}$ and $\npair{[\baddr_2,\eaddr_2]} \in \readCond{\lin,W_2}$.
  \item If $\npair{A} \in \writeCond{\lin,W}$, then there exists $W_1, W_2$ such that $W = W_1\oplus W_2$ such that $\npair{[\baddr_1,\eaddr_1]} \in \writeCond{\lin,W_1}$ and $\npair{[\baddr_2,\eaddr_2]} \in \writeCond{\lin,W_2}$.
  \item If $\npair{A} \in \execCond{\lin,W}$, then there exists $W_1, W_2$ such that $W = W_1\oplus W_2$ such that $\npair{[\baddr_1,\eaddr_1]} \in \execCond{\lin,W_1}$ and $\npair{[\baddr_2,\eaddr_2]} \in \execCond{\lin,W_2}$.
  \end{itemize}
\end{lemma}
\begin{proof}
  TODO
\end{proof}

\begin{lemma}[permission-based conditions shrinkable]
  \label{lem:conds-shrinkable}
  \begin{itemize}
  \item If $\npair{A} \in \readCond{\lin,W}$  and $A' \subseteq A$, then
    $\npair{A'} \in \readCond{\lin,W}$.
  \item If $\npair{A} \in \writeCond{\lin,W}$  and $A' \subseteq A$, then
    $\npair{A'} \in \readCond{\lin,W}$.
  \item If $\npair{A} \in \xReadCond{\lin,W}$  and $A' \subseteq A$, then
    $\npair{A'} \in \xReadCond{\lin,W}$.
  \item If $\npair{A} \in \execCond{\lin,W}$  and $A' \subseteq A$, then
    $\npair{A'} \in \execCond{\lin,W}$.
  \end{itemize}
\end{lemma}
\begin{proof}
  Follows easily from the definition. TODO: check after update
\end{proof}

@@

  then $\npair{(w,w)} \in \lrvg{\trust}(W)$.
\end{lemma}
\begin{proof}
  We distinguish two cases:
  \begin{itemize}
  \item $\trust = \untrusted$ and $\dom(\mscode \mathrel{\#} \ta)$:
    By definition of $\lrv(W)$, it suffices to show that:
    \begin{itemize}
    \item $\npair{[b,e]}\in\readCond{\normal,W}$:
      this follows from Lemma~\ref{lem:code-memory-untrusted-readable}.
    \item $\npair{[b,e]}\in\xReadCond{\normal,W}$:
      follows from the definition of $\xReadCond$, together with the assumption that $\pwheap(r_{\mathrm{code}}) = \codereg{\sigrets,\sigcloss,\mscode,\gc}$.
    \item $\npair{[b,e]}\in\execCond{\normal,W}$:
      take $n' < n$, $W' \future \purePart{W}$, $\aaddr' \in [\baddr',\eaddr'] \subseteq [\baddr,\eaddr]$ and $w' = ((\rx,\normal),\baddr',\eaddr',\aaddr')$.
      Then we need to show that $\npair[n']{(w',w')} \in \lre(W')$.
      This now follows immediately from the (regular) FTLR (Theorem~\ref{thm:ftlr}), using the two above points, Lemma~\ref{lem:downwards-closed} and Lemma~\ref{lem:conds-shrinkable}.
    \end{itemize}
